\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{ragged2e}
\usepackage{blindtext}

\renewcommand{\thesection}{\Roman{section}}
\counterwithout{subsection}{section}
\renewcommand{\thesubsection}{§\arabic{subsection}}

\title{Constitution of the PR Swagistan}
\author{the.god.emperor}
\date{August 20s$^{th}$, 2023}

\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage
\paragraph*{Due to the incompatibility of German law terms with English, `§' has to be read as `act' in the following.}

\section{Basic}
\subsection{Bond of allegiance}
\begin{enumerate}[(1)]
    \item Every citizen must at all times and at all costs protect the dignity and heritage of the PR of Swagistan.
    \item Anyone who turns his back on the nation, whether by giving unauthorised support to an enemy, defecting to it, or leaving and then founding a new nation without the permission of the People's Republic, will be blacklisted.
    \item Any person on the blacklist must be prosecuted and hunted down without exception.
    \item Traitors to the People's Republic should never be forgiven even when showing remorse.
\end{enumerate}

\subsection{Supreme Soviet}
\begin{enumerate}[(1)]
    \item Government decisions are decided by the Supreme Soviet.
    \item The Chairman of the Supreme Soviet is Comrade General Secretary $jaap\_stam$.
    \item Other voting members of the Supreme Soviet are the head of the KGB Comrade $robertogmor$ and the Marshal of Swagistan Comrade $the.god.emperor$.
    \item The heads of departments are also members of the Supreme Soviet, but are not entitled to vote.
    \item In the event of a tie, the General Secretary has a second vote.
\end{enumerate}

\subsection{Armed Forces of the People's Republic of Swagistan}
\begin{enumerate}[(1)]
    \item The armed forces of the People's Republic of Swagistan are responsible for the protection and enforcement of the authority of the People's Republic.
    \item There shall be universal conscription.
    \item The armed forces are headed by the `Armed Forces Command'.
\end{enumerate}

\subsection{Armed Forces Command}
\begin{enumerate}[(1)]
    \item The Armed Forces Command is presided over by the Marshal of Swagistan.
    \item The Armed Forces Command is responsible for the organisation of the army and its operations.
    \item It is superordinate to the Ministry of Defence and the Ministry of War.
\end{enumerate}

\subsection{Arrangements}
\begin{enumerate}[(1)]
    \item The army is structured according to the following hierarchy:
    \begin{enumerate}[(1)]
        \item The \textbf{Marshal of Swagistan} is the Commander-in-Chief of the Army and heads the Armed Forces Command.
        \item The \textbf{Generals of the Divisional Forces} are the commanders of the two Divisional Forces (Attack Forces and Defence Forces).
        \item The \textbf{Colonel-General} is the deputy of a general of a branch of the armed forces.
        \item The \textbf{Colonel} is the commander of troops.
        \item The \textbf{major} is the deputy of the colonel.
        \item The \textbf{lieutenant} is a prospective officer.
        \item The sergeant is an experienced troop member.
        \item \textbf{NCO}
        \item \textbf{Corporal}
    \end{enumerate}
\end{enumerate}

\subsection{Awards}
\begin{enumerate}[(1)]
    \item The Supreme Soviet may confer awards on persons upon nomination.
    \item The awards, their levels and their requirements shall be specified in the Awards Register.
\end{enumerate}

\section{Discord-Server}
\subsection{Behaviour in the chat}\label{verhalten}
\begin{enumerate}[(1)]
	\item $^{1}$Spam, insults, threats and provocations against other players are forbidden and will lead to sanctions. $^{2}$Spamming is the sending of several messages in a short time interval. Sending five or more messages in a short period of time can have consequences. $^{3}$The unauthorised use of pings is also prohibited due to its provocative nature.
	\item $^{1}$Racist, political, ethically unacceptable content (statements, pictures, etc.) are forbidden and will result in permanent exclusion from the entire Discord server. $^{2}$This also applies to pornographic content. $^{3}$This also applies to the deliberate arrangement of reactions to such statements.
	\item Text channels explicitly created for pornographic purposes are excluded from paragraph 2 sentence 2.
	\item \textit{discontinued}
	\item Furthermore, channels may only be used for the purpose for which they are intended. If there are any uncertainties about the intended use, one must contact the support (\ref{support}) before writing a message.
\end{enumerate}

\subsection{Team members}\label{members}
\begin{enumerate}[(1)]
	\item Instructions from commanding team members are binding and must always be followed.
	\item Team members are identified by a rank or role.
	\item Commanding team members include:
	\begin{enumerate}
		\item The General Secretary
		\item The President of the Supreme Court
		\item The Head of the KGB
		\item The Head of Organization
		\item The KGB agents
		\item The Ministers
	\end{enumerate}
    \item The hierarchy mentioned in paragraph 3 is sorted by the rank's authority.
	\item The commanding members may only give orders within their area of responsibility.
\end{enumerate}

\subsection{Behaviour in the voice chat}
\begin{enumerate}[(1)]
    \item Apart from the regulations from~\ref{verhalten}, the following additional regulations apply to voice channels.
	\item The use of voice distorters and soundboards is permitted, provided the team members do not object.
	\item It is not permitted to record persons without their consent.
\end{enumerate}

\subsection{Validity}
\begin{enumerate}[(1)]
	\item By joining this server, you accept the rules set forth herein.
	\item The server administration reserves the right to change these rules at any time.
	\item \textit{discontinued}
	\item The rules only come into force as soon as they are published in the rules text channel. Accordingly, no rule shall apply retroactively.
	\item Lacking or faulty knowledge of the server regulations does not grant legal immunity, as informing oneself about the current legal situation of the server is obligatory.
	\item Likewise, in case of ambiguity, one must contact the person in charge.
	\item If one of the provisions violates the constitution of the country of a person concerned, only the illegal passage is repealed for that person\footnote{salvatory clause}.	
\end{enumerate}

\subsection{Second Accounts}
You have to mark secondary accounts as such. To do this, you have to edit your server profile in such a way that it is possible for everyone to see whose secondary account it is on the basis of this profile.

\subsection{Sentence}
\begin{enumerate}[(1)]
	\item A distinction is generally made between three penalties:
	\begin{enumerate}[(1)]
		\item A warning is a preliminary stage to actual punitive measures. Each member receives a warning for minor offences.
		\item A timeout refers to a temporary exclusion from the server.
		\item A permanent ban is an irrevocable, indefinite exclusion from the server.
	\end{enumerate}
	\item The penalty is rarely assessed according to the severity of the offence, but mostly according to the following:
	\begin{enumerate}[1.]
		\item First warning
		\item Second warning
		\item 24-hour timeout
		\item One-week timeout
		\item One\-month timeout
		\item 1-year timeout
		\item Permanent ban
	\end{enumerate}
	\item Any penalty must be revoked without exception if the punished person can prove the illegality of the penalty.
	\item Unlawfulness exists if the act in question is not an offence on the part of the punished person, if paragraphs 1 and 2 were violated in the punishment or if the act was wrongly classified as an offence of particular gravity.
	\item If the offence is a serious offence, an immediate timeout up to an immediate permanent ban may be imposed depending on the seriousness of the offence. The assessment of the severity is subject to the responsible person, but must be comprehensible. 
	\item If there is any doubt, the judgement may be overturned by the President of the Supreme Court or by a qualified majority vote of the Board and reversed or converted to another penalty.
	\item Any unlawful messages must be stored temporarily in the form of a screenshot until the beginning of the week after next, so that in case of doubt the unlawfulness can be challenged \footnote{This is due to past difficulties in assessing the unlawfulness of statements in retrospect}, after which one can apply to the Board for a deletion, which however must be confirmed by a qualified majority.
    \item After each timeout, the severity of the offence increases in such a way that the first offence after a timeout according to the penalty hierarchy from paragraph 2 number 1 \- 7 is increased due to its severity in relation to the previous basic penalty \footnote{The first penalty after a timeout, respectively the total first penalty.}.
	\item Permanent bans are partly excluded from paragraph 8. These shall only be imposed in cases of extreme severity or where paragraph 8 applies, unless there is an acute improvement in behaviour and the Board votes in favour by a simple majority.
	\item It is not permitted to unban people from the server contrary to the express permission of the President of the Supreme Court. This is considered a punishable offence and will be punished with a timeout regardless of the position in the punishment hierarchy as interpreted in accordance with paragraph 8. The unlawfully unbanned person shall also be banned immediately.
	\item $^{1}$Infractions of particular severity by members of a division will result in permanent expulsion from that and other divisions. $^{2}$This rule does not apply to $jaap\_stam$, $robertogmor$ and $the.god.emperor$ and their secondary accounts.
	\item Complicity, aiding and abetting, incitement and attempt are punished equivalently.
\end{enumerate}

\subsection{Holder}
\begin{enumerate}[(1)]
	\item The term holder corresponds to the term part-owner according to §3 paragraph 1 TOO.
	\item Any resolutions of the Holders shall require a qualified majority unless the Terms of Ownership conflict therewith.
	\item At the direction of the Holders, an Admins' Council may be convened at which the Admins and Moderators who are not Holders shall each be given one vote and shall take the decision for the Holders' Meeting.
\end{enumerate}

\subsection{Chairmanship}
\begin{enumerate}[(1)]
	\item The chairmanship of the Executive Board pursuant to §8 paragraph 2 TOO shall be held by the General Secretary.
	\item It is permanently occupied by $jaap\_stam$.
	\item Should he resign from the board, he has to choose his successor or the new chairman of the board is elected by the board by a simple minority vote.
\end{enumerate}

\subsection{Departments}
\begin{enumerate}[(1)]
	\item The following divisions according to §9 TOO exist on the server:
		\begin{enumerate}[1.]
			\item Department of Organization
			\item Ministry of Justice
			\item Ministry of Defense
			\item Ministry of War
			\item KGB
			\item Ministry of Foreign Affairs
			\item Ministry of Mining and Ore Gathering
			\item Ministry of Agriculture and Food Gathering
			\item Ministry of Adventuring and Loot Gathering
			\item Ministry of Infrastructure and Building
			\item Ministry of Trading and Villagers
			\item Ministry of Finances
			\item Ministry of Technology
			\item Diplomatic guard
		\end{enumerate}
	\item The chairperson of these departments shall be assigned the appropriate role.
	\item Only persons with sufficient knowledge and skills in the respective field may be employed in the divisions.
\end{enumerate}

\subsection{Department of Organization}
\begin{enumerate}[(1)]
    \item The Department of Organization is responsible for properly organizing the server.
    \item This includes role assignment and role management.
    \item The chairmanship of the Department of Organization shall be held by the Head of the Department of Organization (HDO).
\end{enumerate}

\subsection{Ministry of Justice}
\begin{enumerate}[(1)]
	\item The remit of the Ministry of Justice shall include:
	\begin{enumerate}[(1)]
		\item Legal questions concerning the server constitution
		\item Requests for legal assistance
		\item challenges to server court and other rulings
		\item Constitutional complaints
		\item Proposed legislation
		\item Handling of violations of server policies
		\item dealing with breaches of the Terms of Ownership
		\item Examination of moderation judgements
	\end{enumerate}
    \item Proposals for legislation that speak of amending or abolishing already existing legislation are considered constitutional complaints.
	\item Both statutory violations and appeals, as well as constitutional complaints, are considered sufficient grounds for a full trial.
	\item The chairperson of the ministry is the Minister of Justice (MoJ).
	\item In its judicial capacity, the Ministry of Justice is referred to as the `Supreme Court'.
	\item Members of the Supreme Court bear the official title of `Supreme Judge'. Outside of their judicial duties, they are referred to as `server lawyers'.
	\item The High Court is presided over by the President of the Supreme Court.
    \item The President at the Supreme Court shall be the MoJ.\@
	\item Unless there is sufficient new evidence, paragraph 3 does not apply.
	\item Judgments by the Moderation and the Supreme Court must be confirmed by the President at the Supreme Court and may therefore be dismissed.
	\item The dismissal of judgments must be justified and reasoned.
\end{enumerate}

\subsection{Ministry of Defence}
\begin{enumerate}[(1)]
    \item The Ministry of Defence is responsible for protecting the PR of Swagistan.
    \item Members of this Ministry shall be members of the Defence Forces.
    \item The Minister of Defence (MoD) is the Chairman of the Ministry.
\end{enumerate}

\subsection{Ministry of War}
\begin{enumerate}[(1)]
    \item The Ministry of War is responsible for executing attack plans and hunting down blacklisted individuals.
    \item This also includes griefing or any other acts of sabotage.
    \item The Ministry is chaired by the Minister of War (MoW).
\end{enumerate}

\subsection{KGB}\label{support}
\begin{enumerate}[(1)]
	\item Any questions regarding the Discord and Minecraft server that do not fall into the legal area are the responsibility of the KGB. If there are any uncertainties regarding the area of responsibility, you should also contact the moderation.
	\item The KGB serves to control compliance with the server guidelines.
	\item This implies that they are able to enforce penalties without an authorisation, but these have to be forwarded to the Ministry of Justice along with the context and have to be finally confirmed.
	\item The board of moderation is held by the head of the KGB, who also performs administrative tasks.
	\item Excluded from paragraph 3 are any breaches of the Terms of Ownership, as these will be dealt with by the Ministry of Justice and VIRTSTAX.
	\item Members of the moderation will be listed as `KGB agent'.
\end{enumerate}

\subsection{Ministry of Foreign Affairs}
\begin{enumerate}[(1)]
    \item The Ministry of Foreign Affairs is responsible for both inter-factional trade and diplomacy.
    \item This includes the dispatch of diplomats.
    \item The Minister of Foreign Affairs (MoFA) is the Chairman of the Ministry.
\end{enumerate}

\subsection{Ministry of Mining and Ore Gathering}
\begin{enumerate}[(1)]
    \item The Ministry of Mining and Ore Gathering shall be responsible for the mining of ores and other materials typical of the subsoil.
    \item The Chairman of this Ministry is the Minister of Mining and Ore Gathering (MoMOG).
\end{enumerate}

\subsection{Ministry of Agriculture and Food Procurement}
\begin{enumerate}[(1)]
    \item The Ministry of Agriculture and Food Procurement is responsible for growing and organising food.
    \item The Ministry is chaired by the Minister of Agriculture and Food Procurement (MoAFG).
\end{enumerate}

\subsection{Ministry of Exploration and Loot Procurement}
\begin{enumerate}[(1)]
    \item The Ministry of Exploration and Loot Acquisition is responsible for the exploration of areas.
    \item This includes the search for structures and its looting.
    \item The chairman of this ministry is the Minister of Exploration and Loot Procurement (MoALG).
\end{enumerate}

\subsection{Ministry of Infrastructure and Construction}
\begin{enumerate}[(1)]
    \item The Ministry of Infrastructure and Construction is responsible for the construction of buildings.
    \item The Minister of Infrastructure and Construction (MoIB) is the Chairman of the Ministry.
\end{enumerate}

\subsection{Ministry of Commerce and Villagers}
\begin{enumerate}[(1)]
    \item The Ministry of Trade and Villagers shall be responsible for the stocks of and trade with villagers.
    \item The Chairman of this Ministry is the Minister of Trade and Villagers (MoTV).
\end{enumerate}

\subsection{Ministry of Finances}
\begin{enumerate}[(1)]
	\item The Ministry of Finances is responsible for keeping track of the server finances.
	\item This also involves the management of the company's shares.
	\item The Minister of Finances (MoF) is the stock transaction trustee according to §7 TOO.\@
\end{enumerate}

\subsection{Ministry of Technology}
\begin{enumerate}[(1)]
	\item The Ministry of Technology serves to maintain all servers and services under rule of the PR Swagistan.
	\item This also includes the realisation of new functionalities on these.
	\item It is chaired by the Minister of Technology (MoT).
	\item Members of this department are called `technicians'.
\end{enumerate}

\subsection{Diplomatic Guard}
\begin{enumerate}[(1)]
	\item The Diplomatic Guard serves to escort diplomatic envoys.
	\item It reports directly to the Ministry of Foreign Affairs.
\end{enumerate}

\section{Minecraft-Server}

\subsection{Application}
The acts of this section shall only apply when the PR Swagistan holds any server.

\subsection{Guarantee}
\begin{enumerate}[(1)]
	\item Only persons for whom someone can be proved to be a guarantor may be placed on the whitelist.
	\item If a person commits a violation of particular severity, he/she will be banned from the server along with the guarantor.
	\item If a guarantor is banned from the server, this is done equally to those for whom the guarantor stands surety.
	\item Guarantees cannot be withdrawn afterwards.
	\item The administration is exempted from paragraph 2f.
\end{enumerate}

\subsection{Legal separation}
\begin{enumerate}[(1)]
	\item The server right shall be clearly distinguished from the internal right situation on the offshoots of The God Complex Server.
	\item Internal law refers to constitutions and rules, such as faction-owned legal texts, that are not recognised by the proprietorship in its function as a proprietary assembly.
	\item The inspection and use of server data and other information accessible only to the administration, such as player data or logs, which are superior to internal regulations, may not be used as evidence for trials and the like which are not carried out by the Supreme Server Court in its function\footnote{For example, in-game murders may not be proven via logs}.
\end{enumerate}

\subsection{Basic rules}
\begin{enumerate}[(1)]
	\item The Minecraft server right is subject to the Discord server right.
	\item It is forbidden to resort to methods that give an advantage over other players, regardless of whether they use the method or not, that are not generally recognised as fair.
	\item Any behaviour not affected by such methods is not punishable.
	\item On the Minecraft server, one must behave according to the respective Discord server rules.
	\item The general server law does not differentiate between factions, which is why this is merely an internal organisation that is not covered by any server-wide laws and thus crimes against them in detail cannot be subject to server-wide judgements.
	\item 3 only applies if the offences are not against the rules of the Discord server or para 1f.
\end{enumerate}

\subsection{Factions}
\begin{enumerate}[(1)]
    \item A faction is any grouping with more than one player.
	\item The term player is not synonymous with the term Minecraft account and therefore does not warrant creation if the other account is a secondary account of the person.
	\item Factions have the right to their own category in which they can create any channels upon request.
	\item The moderation may reject such requests unless they can establish a justifiable reason for setting them up.
	\item Due to the activity and tasks of the moderation, the moderation is entitled to look into the channels at any time in order to be able to identify violations of the applicable law.
	\item Each parliamentary group is granted its own role, the purpose of which is to ensure that these channels cannot be viewed by members of other parliamentary groups.
\end{enumerate}

\subsection{Specific server law}
\begin{enumerate}[(1)]
    \item It is forbidden to destroy places that are a place of knowledge.
	\item Paragraph 1 may only be broken if a faction exploits this rule to gain an advantage.
	\item Each faction must claim a territory when it is established.
	\item This territory must consist of an above-ground biome and may not initially extend beyond its boundaries.
	\item Only materials originating from this territory or acquired from others may be used.
	\item One may extend one's territory to a neighbouring biome with each extension announced server-wide by the administration according to par. 3ff.
	\item Different variants of a biome are not considered to be its own biome.
\end{enumerate}

\end{document}