\documentclass{cjs9}
\usepackage[utf8]{inputenc}
\usepackage{enumerate}
\usepackage{ragged2e}
\usepackage{etoc}

\title{Declaration of the new Rex Novus Guidelines}
\author{Elias N. Jetzinger}
\date{09. April 2024}

\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage
\section{Basis}
\newpage
\section{Message Reaction Act}
\decision{July \ordinalnum{19}, 2023}
\subsection{Declaration}
\paragraph{Since 6 February 2023 in the office of Judge and since March of the same year appointed as President of the Supreme Server Court and thus with extensive powers to execute his office as the legislative and judicial power of the server and all its subordinate instances, any orders of the Supreme Server Judge are made on the authority of the Server Council.\\}
The following document has been written retrospectively due to time constraints. On 13 July 2023, a complaint was received against server member Bennet (Discord ID: 642406046836719656) for violation of §1 para. 2 DR. The subject of the complaint was the stringing together of reactions of the category "Regional Indicator" to the word "PENIS". After a thorough examination of the irregularity of this behaviour by the Supreme Server Court, it was determined that the definition of "ethically unacceptable content" or "statements" only applied to a limited extent in this case and no longer corresponded to its actual definition.
\\In this process, the Supreme Server Court also pointed out that the deliberate ordering of reactions to ethically unacceptable statements should now be illegal.
\\For the reasons stated, the complaint pursuant to §8 para. 8 is rejected and all proceedings in this regard are to be discontinued with immediate effect.
\\\\This decision may be contested in accordance with §8 para. 1 No. 3 DR.
\subsection{Changes}
\subsubsection*{§2 para. 2, clause 3}
This also applies to the deliberate arrangement of reactions in the "Regional Indicator" category to such statements.
\newpage
\section{Channel Usage Act}
\decision{Februar \ordinalnum{12}, 2023}
\subsection{Declaration}
\textit{(No original declaration issued. The following declaration was made retrospectively and retroactively for the guidelines of the Rex Novus SMP on 12 April 2024 by order of The God Complex Servers Ownership.)\\\\}
Due to multiple instances of misuse of chat platforms designed for text messages through the sending of GIFs and the complications arising from it, it was decided on February 12, 2023, utilizing the authority granted by the Chief Server Judge (§2 para. 1), that separate channels should be established for these purposes and GIFs should not be sent outside of these channels.
\\This decision was made specifically in response to incidents where important messages were overlooked as individuals overloaded the channel with distracting GIFs.
\subsection{Changes}
\subsubsection*{§2 para. 2, clause 4}
The sending of GIFs is prohibited.
\newpage
\section{Channel Usage Act Amendment}
\decision{March \ordinalnum{15}, 2024}
\subsection{Declaration}
\paragraph{By order of The God Complex Servers domain owners\\}
The Channel Usage Act was expanded on the order of ownership on March 15, 2024, to allow the description of channels as legally valid references for determining channel usage purposes.
\\The order is intended to definitively guarantee the adaptability of the current channel usage policies.
\subsection{Changes}
\subsubsection*{§2 para. 5, clause 2}
One must also adhere to the description of the channels and their correct usage of functions.

\newpage
\section{Anti-Extremism Act}
\decision{February \ordinalnum{20}, 2024}
\subsection{Declaration}
\paragraph{By order of the The God Complex Servers domain owners\\}
In an effort not to jeopardise or impair the cohesion of our community by spreading harmful political opinions, the domain owners of The God Complex Servers have unanimously decided to extend the existing ban on right-wing extremist statements in the Federal Republic of Germany to include a ban on left-wing extremist statements.
\\Not only do we utterly despise and disapprove of the actions of National Socialist and fascist regimes, movements and terrorist cells, we also do the same with communist, anarchist and other anti-democratic movements.
\\It remains to be made clear that statements critical of democracy are tolerated as long as they neither call for violence nor trivialise it or the actions of historical or current extremist groups.
\\Fundamental to this decision is the realisation that Marxism, Leninism and especially Stalinism, as well as Maoism, are just as opposed to the basic democratic order as National Socialism and fascism. It should also be noted that Stalinism is responsible for a number of atrocities on a scale that approaches, if not equals, the deeds of National Socialism.
\\The server owners are of the opinion that this restriction of freedom of speech is a necessary measure to guarantee political openness and democracy-based debate.\subsection{Changes}
\subsubsection*{§2 para. 2, clause 5}
Symbols and trivialisation of any politically extremist acts or groups are prohibited.
\newpage
\section{Domain Security Act}
\decision{March \ordinalnum{29}, 2024}
\subsection{Declaration}
\paragraph{By order of the The God Complex Servers domain owners\\}
In conjunction with the development of advanced moderation tools for the domains under the supervision of the VIRTSTAX Administration and The God Emperor Networks, the domain ownership of The God Complex Servers decided on March 29, 2024, to introduce an administrative area specialized in ensuring the security of domain assets and domain services.
\\To effectively fulfill its duties, the security department, which is now under the jurisdiction of the Chief Security Officer (CSO), is granted comprehensive powers. Any operations require only the approval of the CEOs and may not be disclosed to other individuals until approved, including those working within the department who have not been assigned to the project.
\subsection{Changes}
\subsubsection*{§3 para. 3 No. 3}
The CSO
\subsubsection*{§14 Security department}
\begin{enumerate}[(1)]
    \item The security department serves to safeguard the domain owners and monitor user activities.
    \item Any means to fulfill their tasks must be approved solely by the acting CEOs.
    \item The Chief Security Officer (CSO) holds the chairmanship.
    \item The operations within this department are subject to strict confidentiality and may only be disclosed with the permission of the CEOs.
\end{enumerate}
\newpage
\section{Criminal Records Act}
\decision{March \ordinalnum{15}, 2024}
\subsection{Declaration}
\paragraph{By order of the The God Complex Servers domain owners\\}
As a result of past difficulties in subsequently checking infringement reports for their actual irregularity, the domain owners have decided that from now on there will be a general recording obligation in the form of screenshots and screen recordings. 
\\In addition, it was decided that these entries should a) be permanent so that they can be re-evaluated in the future if necessary and b) also be recorded in a criminal record.
\\Since the introduction of the VIRTSTAX Global Platform, there has been a general obligation to use the watchlist as a criminal record.
\subsection{Changes}
\subsubsection*{§6 para. 7}
Any unlawful messages must be permanently stored in the criminal record in the form of a screenshot together with the description of the incident so that the unlawfulness can be contested in case of doubt, after which a request for deletion can be made to the Board of Directors, which must be confirmed by a qualified majority.
\newpage
\section{Prejudice Act}
\decision{March \ordinalnum{17}, 2024}
\subsection{Declaration}
In order to prevent ambiguous and therefore potentially dangerous and counterproductive interpretations of the guidelines by actual offenders, the legal department was given the ability to determine the interpretation and interpretation of existing laws by order of the domain owner.
\\However, this must a) be within a justifiable and comprehensible framework, b) be applied to existing laws and not used to create new laws, and c) be clearly consistent with previous decisions on the interpretation of these and other laws by the legal department.
\subsection{Changes}
\subsubsection*{§11 para. 12}
The legal department is able to use judgements to determine the interpretation of
individual laws by means of judgements, provided this is within a comprehensible
framework.
\newpage
\section{Guarantee Act}
\decision{June \ordinalnum{30}, 2023}
\subsection{Declaration}
\textit{Excerpt of the original declaration\\}
[\dots] Furthermore, all members who propose new members for the project are obliged to vouch for them. This means that if the person you are vouching for commits server law offences, you will also be excluded from the project. If the guarantor is excluded from the project, all those for whom he or she vouches will also be excluded. [\dots]
\subsection{Changes}
\subsubsection*{§15 Guarantee}
\begin{enumerate}[(1)]
    \item Only persons who can be proven to be vouched for may be placed on the whitelist.
    \item If a person commits an offence of particular severity, they will be banned from the server along with the guarantor.
    \item If a guarantor is banned from the server, this happens in the same way to those for whom they are vouching.
    \item Guarantees cannot be withdrawn retrospectively.
    \item The administration is immune to para. 2 and 3.
\end{enumerate}
\newpage
\section{Guarantee Act Amendment}
\decision{February \ordinalnum{20}, 2024}
\subsection{Declaration}
\paragraph{By order of the The God Complex domain owners\\}
In order to ensure that no guarantors who are not at fault for the guarantor's actions and no guarantors who are not at fault for the guarantor's actions are prematurely and unlawfully banned, the domain owners have agreed to amend the guarantee conditions.
\\From now on, a) guarantee relationships must be reviewed in the event of offences of particular severity and cancelled if necessary and b) in the event of permanent exclusion or cancellation of the guarantor's guarantee relationships, all guarantees that they have made lose their validity. 
\subsection{Changes}
\subsubsection*{§15 para. 2}
If a person commits an offence of particular gravity, the existing guarantee relationships are reviewed and can be cancelled if necessary.
\subsubsection*{§15 para. 3}
If a guarantor is banned from the server, all guarantee relationships with this guarantor are terminated.
\newpage
\section{Faction Establishment Act}
\decision{February \ordinalnum{20}, 2024}
\subsection{Declaration}
\subsection{Changes}
\newpage
\section{Faction Establishment Act Amendment}
\decision{February \ordinalnum{26}, 2024}
\subsection{Declaration}
\subsection{Changes}
\newpage
\section{Faction Establishment Act Amendment II}
\decision{March \ordinalnum{24}, 2024}
\subsection{Declaration}
\subsection{Changes}
\newpage
\section{War Regulatory Act}
\decision{June \ordinalnum{02}, 2023}
\subsection{Declaration}
\subsection{Changes}
\newpage
\section{War Regulatory Act Amendment}
\decision{February \ordinalnum{21}, 2024}
\subsection{Declaration}
\subsection{Changes}
\newpage
\section{War Regulatory Act Amendment II}
\decision{February \ordinalnum{28}, 2024}
\subsection{Declaration}
\subsection{Changes}
\end{document}