\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{ragged2e}
\usepackage{blindtext}

\renewcommand{\thesection}{\Roman{section}}
\counterwithout{subsection}{section}
\renewcommand{\thesubsection}{§\arabic{subsection}}

\title{Guidelines of The God Complex Servers}
\author{the.god.emperor}
\date{August 23$^{rd}$, 2023}

\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage
\paragraph*{Due to the incompatibility of German law terms with English, `§' has to be read as `act' in the following.}

\section{Discord-Server}
\subsection{Behaviour in the chat}\label{verhalten}
\begin{enumerate}[(1)]
	\item $^{1}$Spam, insults, threats and provocations against other players are forbidden and will lead to sanctions. $^{2}$Spamming is the sending of several messages in a short time interval. Sending five or more messages in a short period of time can have consequences. $^{3}$The unauthorised use of pings is also prohibited due to its provocative nature.
	\item $^{1}$Racist, political, ethically unacceptable content (statements, pictures, etc.) are forbidden and will result in permanent exclusion from the entire Discord server. $^{2}$This also applies to pornographic content. $^{3}$This also applies to the deliberate arrangement of reactions of the category "Regional Indicator" to such statements. $^{4}$Sending GIFs is prohibited.
	\item Text channels explicitly created for pornographic purposes are excluded from paragraph 2 sentence 2.
	\item Text channels intended for memes are exempt from paragraph 2, sentence 4.
	\item Furthermore, channels may only be used for the purpose for which they are intended. If there are any uncertainties about the intended use, one must contact the support (\ref{support}) before writing a message.
\end{enumerate}

\subsection{Team members}\label{members}
\begin{enumerate}[(1)]
	\item Instructions from commanding team members are binding and must always be followed.
	\item Team members are identified by a rank or role.
	\item Commanding team members include:
	\begin{enumerate}
		\item The CEO
		\item The CLO
		\item The Owners
		\item The Founders
		\item The COO
		\item The CTO
		\item The CAO
		\item The Technicians
		\item The DC-Moderators
		\item The MC-Moderators
	\end{enumerate}
	\item The commanding members may only give orders within their area of responsibility.
\end{enumerate}

\subsection{Behaviour in the voice chat}
\begin{enumerate}[(1)]
    \item Apart from the regulations from~\ref{verhalten}, the following additional regulations apply to voice channels.
	\item The use of voice distorters and soundboards is permitted, provided the team members do not object.
	\item It is not permitted to record persons without their consent.
\end{enumerate}

\subsection{Validity}
\begin{enumerate}[(1)]
	\item By joining this server, you accept the rules set forth herein.
	\item The server administration reserves the right to change these rules at any time.
	\item \textit{discontinued}
	\item The rules only come into force as soon as they are published in the rules text channel. Accordingly, no rule shall apply retroactively.
	\item Lacking or faulty knowledge of the server regulations does not grant legal immunity, as informing oneself about the current legal situation of the server is obligatory.
	\item Likewise, in case of ambiguity, one must contact the person in charge due to\ref{members}.
	\item If one of the provisions violates the constitution of the country of a person concerned, only the illegal passage is repealed for that person\footnote{salvatory clause}.	
\end{enumerate}

\subsection{Second Accounts}
You have to mark secondary accounts as such. To do this, you have to edit your server profile in such a way that it is possible for everyone to see whose secondary account it is on the basis of this profile.

\subsection{Sentence}
\begin{enumerate}[(1)]
	\item A distinction is generally made between three penalties:
	\begin{enumerate}[(1)]
		\item A warning is a preliminary stage to actual punitive measures. Each member receives a warning for minor offences.
		\item A timeout refers to a temporary exclusion from the server.
		\item A permanent ban is an irrevocable, indefinite exclusion from the server.
	\end{enumerate}
	\item The penalty is rarely assessed according to the severity of the offence, but mostly according to the following:
	\begin{enumerate}[1.]
		\item First warning
		\item Second warning
		\item 24-hour timeout
		\item One-week timeout
		\item One\-month timeout
		\item 1-year timeout
		\item Permanent ban
	\end{enumerate}
	\item Any penalty must be revoked without exception if the punished person can prove the illegality of the penalty.
	\item Unlawfulness exists if the act in question is not an offence on the part of the punished person, if paragraphs 1 and 2 were violated in the punishment or if the act was wrongly classified as an offence of particular gravity.
	\item If the offence is a serious offence, an immediate timeout up to an immediate permanent ban may be imposed depending on the seriousness of the offence. The assessment of the severity is subject to the responsible person, but must be comprehensible. 
	\item If there is any doubt, the judgement may be overturned by the CLO or by a qualified majority vote of the Board and reversed or converted to another penalty.
	\item Any unlawful messages must be stored temporarily in the form of a screenshot until the beginning of the week after next, so that in case of doubt the unlawfulness can be challenged \footnote{This is due to past difficulties in assessing the unlawfulness of statements in retrospect}, after which one can apply to the Board for a deletion, which however must be confirmed by a qualified majority.
    \item After each timeout, the severity of the offence increases in such a way that the first offence after a timeout according to the penalty hierarchy from paragraph 2 number 1 \- 7 is increased due to its severity in relation to the previous basic penalty \footnote{The first penalty after a timeout, respectively the total first penalty.}.
	\item Permanent bans are partly excluded from paragraph 8. These shall only be imposed in cases of extreme severity or where paragraph 8 applies, unless there is an acute improvement in behaviour and the Board votes in favour by a simple majority.
	\item It is not permitted to unban people from the server contrary to the express permission of the CLO. This is considered a punishable offence and will be punished with a timeout regardless of the position in the punishment hierarchy as interpreted in accordance with paragraph 8. The unlawfully unbanned person shall also be banned immediately.
	\item $^{1}$Infractions of particular severity by members of a division will result in permanent expulsion from that and other divisions. $^{2}$This rule does not apply to the.god.emperor or his secondary accounts.
	\item Complicity, aiding and abetting, incitement and attempt are punished equivalently.
\end{enumerate}

\subsection{Holder}
\begin{enumerate}[(1)]
	\item The term holder corresponds to the term part-owner according to §3 para. 1 ToO.
	\item Any resolutions of the Holders shall require a qualified majority unless the Partnership Rules conflict therewith.
	\item At the direction of the Holders, an Admins' Council may be convened at which the Admins and Moderators who are not Holders shall each be given one vote and shall take the decision for the Holders' Meeting.
\end{enumerate}

\subsection{Chairmanship}
\begin{enumerate}[(1)]
	\item The chairmanship of the Executive Board pursuant to §8 para. 2 ToO shall be held by the Chief executive officer. This rank designation is abbreviated as 'CEO'.
	\item It is permanently occupied by the founder of the server.
	\item The founder is $the.god.emperor$ (705020938810294392).
	\item Should both founders resign from the board, a new chairman of the board must be elected by the board by a simple minority vote.
\end{enumerate}

\subsection{Business Units}
\begin{enumerate}[(1)]
	\item The following divisions according to §9 ToO exist on the server:
		\begin{enumerate}[(1)]
			\item Bookkeeping (Accounting)
			\item Legal Department (Legal Department)
			\item Moderation
			\item Technical Department
		\end{enumerate}
	\item The chairperson of these departments shall be assigned the appropriate role.
	\item Only persons with sufficient knowledge and skills in the respective field may be employed in the divisions.
\end{enumerate}

\subsection{Accounting}
\begin{enumerate}[(1)]
	\item The accounting department is responsible for keeping track of the server finances.
	\item This also involves the management of the company's shares.
	\item The Chief accounting officer (CAO) is the transactional officer according to §7 ToO and the head of department.
\end{enumerate}

\subsection{Legal}
\begin{enumerate}[(1)]
	\item The remit of the Legal Department shall include:
	\begin{enumerate}[(1)]
		\item Legal questions concerning the server constitution
		\item Requests for legal assistance
		\item challenges to server court and other rulings
		\item Constitutional complaints
		\item Proposed legislation
		\item Handling of violations of server policies
		\item dealing with breaches of the partnership rules
		\item Examination of moderation judgements
	\end{enumerate}
    \item Proposals for legislation that speak of amending or abolishing already existing legislation are considered constitutional complaints.
	\item Both statutory violations and appeals, as well as constitutional complaints, are considered sufficient grounds for a full trial.
	\item The chairperson of the department is the chief legal officer (CLO).
	\item In its judicial capacity, the Legal Division is referred to as the `Supreme Court'.
	\item Members of the Supreme Court of Servers bear the official title of `Supreme Judge'. Outside of their judicial duties, they are referred to as 'server lawyers'.
	\item The High Court is presided over by the President of the Supreme Court.
    \item The President at the Supreme Court shall be the CLO.\@
	\item Unless there is sufficient new evidence, paragraph 5 does not apply.
	\item Judgments by the Moderation and the Supreme Court must be confirmed by the President at the Supreme Court and may therefore be dismissed.
	\item The dismissal of judgments must be justified and reasoned.
\end{enumerate}

\subsection{Moderation}\label{support}
\begin{enumerate}[(1)]
	\item Any questions regarding the Discord and Minecraft server that do not fall into the legal area are the responsibility of the moderation. If there are any uncertainties regarding the area of responsibility, you should also contact the moderation.
	\item The moderation department serves to control compliance with the server guidelines.
	\item This implies that they are able to enforce penalties without an authorisation, but these have to be forwarded to the legal department along with the context and have to be finally confirmed.
	\item The board of moderation is held by the chief operating officer (COO), who also performs administrative tasks.
	\item Excluded from paragraph 3 are any breaches of the partnership rules, as these will be dealt with by the legal department and VIRTSTAX.
	\item Members of the moderation will be listed as 'MC Moderator' (Minecraft Moderator) or as 'DC Moderator' (Discord Moderator) depending on their area of responsibility.
	\item Moderators may only enforce judgements under paragraph 3 within their area of responsibility.
	\item Minecraft moderators, unlike Discord moderators, do not have Discord administrator privileges, but do have operator privileges on the Minecraft server.
\end{enumerate}

\subsection{Technical Department}
\begin{enumerate}[(1)]
	\item The technical department serves to maintain all servers and services under The God Complex Servers.
	\item This also includes the realisation of new functionalities on these servers.
	\item It is chaired by the Chief Technology Officer (CTO).
	\item Members of this department are called 'technicians'.
\end{enumerate}

\section{Minecraft-Server}

\subsection{Legal separation}
\begin{enumerate}[(1)]
	\item The server right shall be clearly distinguished from the internal right situation on the offshoots of The God Complex Server.
	\item Internal law refers to constitutions and rules, such as faction-owned legal texts, that are not recognised by the proprietorship in its function as a proprietary assembly.
	\item The inspection and use of server data and other information accessible only to the administration, such as player data or logs, which are superior to internal regulations, may not be used as evidence for trials and the like which are not carried out by the Supreme Server Court in its function\footnote{For example, in-game murders may not be proven via logs}.
\end{enumerate}

\subsection{Basic rules}
\begin{enumerate}[(1)]
	\item The Minecraft server right is subject to the Discord server right.
	\item It is forbidden to resort to methods which give an advantage over other players, whether or not the others also use that method, which is not generally recognised as fair.
	\item Any behaviour not affected by such methods is not punishable.
	\item Excluded from paragraph 3 is the construction of structures that serve the purpose of reducing server performance.
	\item On the Minecraft server, one must behave according to the respective Discord server rules.
	\item The general server law does not differentiate between factions, which is why this is merely an internal organisation that is not covered by any server-wide laws and thus crimes against them in detail cannot be subject to server-wide judgements.
	\item 3 only applies if the offences are not against the rules of the Discord server or para 1f.
\end{enumerate}

\subsection{Factions}
\begin{enumerate}[(1)]
    \item A faction is any grouping with more than one player that has properly registered on the \#apply-for-a-team forum channel.
	\item The term player is not synonymous with the term Minecraft account and therefore does not warrant creation if the other account is a secondary account of the person.
	\item Factions have the right to their own category in which they can create any channels upon request.
	\item The moderation may reject such requests unless they can establish a justifiable reason for setting them up.
	\item Due to the activity and tasks of the moderation, the moderation is entitled to look into the channels at any time in order to be able to identify violations of the applicable law.
	\item Each faction is granted its own role, the purpose of which is to ensure that these channels cannot be viewed by members of other faction.
\end{enumerate}

\end{document}