\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{enumerate}
\usepackage{ragged2e}
\usepackage{blindtext}

\renewcommand{\thesection}{\Roman{section}}
\counterwithout{subsection}{section}
\renewcommand{\thesubsection}{ยง\arabic{subsection}}

\title{Terms of Ownership (ToO)}
\author{VIRTSTAX}
\date{August 23$^{rd}$, 2023}

\begin{document}
\maketitle
\newpage
\tableofcontents
\newpage
\subsection{Basic provisions}
\begin{enumerate}[(1)]
	\item The use of the Partnership Rules requires that the server structure conforms to the latest version of the Specifications, as well as an official partnership with VIRTSTAX.\@
	\item In order for the Partnership Rules to take legal effect, their implementation must be clearly approved in writing by the server owner, according to Discord.
	\item For approval it is sufficient that the server owner has uploaded these basic provisions on the Discord concerned.
\end{enumerate}

\subsection{Rights of the owner according to Discord or other platforms}
\begin{enumerate}[(1)]
	\item As soon as the owner sells shares in his Discord server or other services of his organisation, he loses the rights to the sold shares completely and thus has only a partial ownership.
	\item This includes that the server owner loses the right to invoke his status as original founder or by transferring ownership through the method provided by Discord or other platforms, thus justifying a sole or non-share voting right.
	\item A server deletion must also be approved by a majority of all Shareholders.
\end{enumerate}

\subsection{General property rights}
\begin{enumerate}[(1)]
	\item All persons who have acquired VIRTSTAX-certified shares in the organisation shall be full shareholders for the period during which the shares are valid.
	\item If one has not acquired these shares in accordance with paragraph 1, one has no share rights in the organisation.
	\item Their voting rights shall be equal to their shares in the organisation. $^{2}$This also implies that they shall assume liability for the organisation commensurate with their shares and shall be held accountable in the event of legal proceedings commensurate with their shares.
	\item $^{1}$Shareholders with at least 25.1\% are considered to be the main leaders of the organisation and can prevent resolutions with a required qualified minority. $^{2}$In legal matters, they are the leaders of the organisation and accordingly have to answer for legal problems in court or other committees.
	\item As a full holder of the shares, one can resell the shares without approval from other shareholders, but must inform VIRTSTAX regarding the sale and authorise the sale.
	\item VIRTSTAX may refuse the sale only if the shares no longer correspond in accuracy or authenticity to the shares originally purchased, the recipient of the shareholding has been entered on the organisation's or VIRTSTAX's list of prohibited recipients, or the price is less than the basic share value.
	\item Similarly, the Shareholder decides the cost of their Shares, but the Meeting of Holders may decide by a simple majority that such Shares must be equal to the average share prices for the month. Members may not exercise the rights in the first sentence of paragraph 3 when making this decision. Likewise, said shareholder shall not be entitled to vote on this decision.
	\item The seller is obliged to pay the basic share value to the organisation whose shares he has sold.
	\item Shareholders shall have a release for all documents and other information of the organisation, but shall not disclose them to persons who do not have a release for the information in question without the authorisation of the competent body.
	\item The right to information described in paragraph 8 does not apply to structurally critical information, such as access to the root user of a server. Such information may only be lent to technical staff and the board chair.
	\item 8 may be denied provided there is a justified, credible and demonstrable interest in retaining the information.
	\item owners may not be forced to sell their shares or otherwise be excluded from the board unless there are violations of applicable policies of the organisation by the shareholder that would justify such action.
\end{enumerate}

\subsection{Basic share value}
The basic share value refers to the minimum value of a share. These are one thousandth of the total costs incurred by an organisation each month.

\subsection{Share}
\begin{enumerate}[(1)]
	\item In the Partnership Rules, a share is a document certified by VIRTSTAX which evidences the partnership and its provisions.
	\item The document must contain the following information:
	\begin{enumerate}[1.]
		\item Date of purchase and due date
		\item Written certification by VIRTSTAX
		\item The name of the parent organisation whose shares have been purchased
		\item The registration number of the share: This serves as a reference as to how many shares of this organisation it is that have been certified by VIRTSTAX and also includes the VIRTSTAX abbreviation of the organisation.
		\item The share value: The value of a single share in a currency indicated by the ISO-4217 code.
		\item The number of shares purchased.
		\item A brief description of the share entitlements
		\item The signature of the persons authorised to enter into the transaction, together with their functions in the organisation: only a symbolic signature may be used as a signature, not the actual signature, in order to preserve privacy.
		\item The token: The token is the unique security number that certifies authenticity.
	\end{enumerate}
	\item Only VIRTSTAX may issue shares.
	\item The purchase price shall be rounded in accordance with DIN 1333.
	\item Shares may only be bought and sold on official VIRTSTAX trading venues.
	\item trading venues of organisations that have an official partnership with VIRTSTAX are not official trading venues unless they are registered as such.
\end{enumerate}

\subsection{Participation due date}
\begin{enumerate}[(1)]
	\item Each share is only valid during the period for which one has paid for the shares.
	\item This period is usually measured in months.
	\item One can buy shares for the corresponding amount already for longer periods.
	\item If the validity of a share expires, the shares also expire, which is why they must be reacquired in good time if there is an interest in maintaining the share rights.
	\item The period of validity begins on the day on which the share was issued.
\end{enumerate}

\subsection{Organisation}
In the partnership provisions, an organisation is the superordinate entity in which one acquires shares through the purchase of shares.

\subsection{Transaction Entity}
\begin{enumerate}[(1)]
	\item A transaction beneficiary (referred to on the share as a stock transaction trustee) is the trustee of the shares authorised by the holder and thus authorised to make the issue of free share units.
	\item The transaction trustee is not in a position to stop subsequent share transactions, but nevertheless administers them.
	\item He acts as an intermediary between VIRTSTAX and the seller and must confirm that payment has been received in order for VIRTSTAX to issue the share.
	\item In his absence, an alternate transaction agent must be elected by the board.
\end{enumerate}

\subsection{Board}
\begin{enumerate}[(1)]
	\item The board of directors is the meeting of all shareholders in accordance with the partnership rules.
	\item Any decisions affecting the organisation or subordinate bodies and not specifically falling within individual divisions must be approved by a majority of the board.
	\item The organisation shall be free to regulate the occupancy of the chairmanship of the board.
\end{enumerate}

\subsection{Department}
\begin{enumerate}[(1)]
	\item In organisations, a division is a department responsible for carrying out certain tasks assigned to it by server law.
	\item Decisions that fall within the remit of a division and concern instances that are subordinate to the head of the division or to the division itself may be made without the approval of the board.
	\item However, the Board is able to overrule decisions taken in accordance with paragraph 2 with a qualified majority.
\end{enumerate}
\end{document}